%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Hao-Chun Liang}
\end{center}

 \begin{center}
    \vspace{-3mm}
\small 
\href{mailto:science103555@gmail.com}{\underline{Email}} $|$
\href{https://www.linkedin.com/in/hao-chun-noah-liang-131348207/}{\underline{Linkedin}} $|$ 0982-955885 
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Yang Ming Chiao Tung University}{Sept. 2025 -- Present}
      {Master of Engineering - Institute of Pioneer Semiconductor Innovation $\vert$ Digital IC Design}{Hsinchu, Taiwan}

      
    \resumeSubheading
      {National Tsing Hua University}{Sept. 2021 -- Jun. 2024}
      {Bachelor of Engineering - Electrical Engineering $\vert$ GPA 4.10/4.30 $\vert$ Honor Graduation}{Hsinchu, Taiwan}
      
    \resumeSubheading
      {National Tsing Hua University}{Sept. 2020 -- Jun. 2021}
      {Bachelor of Science - Physics $\vert$ Transferred to the Department of Electrical Engineering}{Hsinchu, Taiwan}

      
  \resumeSubHeadingListEnd


%-----------Work Experience-----------
\section{Work Experience}
  \resumeSubHeadingListStart


      
    \resumeSubheading
      {Hardware and Algorithm Codevelopment - Affiliate Trainee}{Jan. 2025 -- Present}
      {Accelerated AI Algorithms for Data-Driven Discovery}{Washington, U.S. (Remote)}
      
    \resumeSubheading
      {Graduate Research Assistant}{Dec. 2024 -- Present}
      {National Yang Ming Chiao Tung University $\vert$ Institute of Pioneer Semiconductor Innovation}{Hsinchu, Taiwan}
      
    \resumeSubheading
      {AI/Deep Learning Accelerator - Digital Design Intern}{Nov. 2024 -- Present}
      {Acceleration R\&D Division $\vert$ Andes Technology Corporation}{Hsinchu, Taiwan}
      
    \resumeSubheading
      {General Physics Experiment Teaching Assistant}{Sept. 2023 -- Jan. 2024}
      {National Tsing Hua University $\vert$ College of Science}{Hsinchu, Taiwan}

  \resumeSubHeadingListEnd


%-----------Work Experience-----------
\section{Awards}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Certificate of Outstanding Graduate Award (Top 8\% of Class)}{Jun. 2024}      
      {National Tsing Hua University $\vert$ Electrical Engineering}{Hsinchu, Taiwan}
      
    \resumeSubheading
      {College of Science Elite Student Award (1st Place, Freshman Year)}{Apr. 2021}
      {National Tsing Hua University $\vert$ College of Science}{Hsinchu, Taiwan}
      
    \resumeSubheading
      {Three Presidential Awards (Top 5\% Each Semester)}{Jun. 2024}
      {National Tsing Hua University}{Hsinchu, Taiwan}

  

    \resumeSubheading
      {ADFP@TSMC N16 Cell-Based Chip Design Flow}{Sep. 2024}   
      {Taiwan Semiconductor Research Institute $\vert$ TSRI}{Hsinchu, Taiwan}
      
    \resumeSubheading
      {Transformer-Based Natural Language Processing}{Dec. 2023}   
      {Deep Learning Institute $\vert$ NVIDIA}{Hsinchu, Taiwan}

      
  \resumeSubHeadingListEnd


\section{Papers}
  \resumeSubHeadingListStart

    \resumeSubheading
      {HiGTR: High-Performance FPGA for GNN-Based Trajectory Reconstruction in HEP}{}
      {Taiwan and Japan Conference on Circuits and Systems, TJCAS 2025, Second Author}{}
      
    \resumeSubheading
      {A High-Performance Implementation of GNN-Based Trajectory Reconstruction on FPGA}{}   
      {VLSI Design/CAD Symposium 2025, Second Author}{}

    \resumeSubheading
      {Fine-Grained Image Recognition from Scratch with Teacher-Guided Data Augmentation}{}
      {Arxiv, Fifth Author}{}
      
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data-Driven Code Generation for RTL, C, AsciiDoc}{Sep. 2025}   
      {Acceleration R\&D Division $\vert$ Andes Technology Corporation}{Hsinchu, Taiwan}
  
    \resumeSubheading
      {RISC-V Five-Stage Pipelined Featuring Stall and Forwarding Control}{Jan. 2024}   
      {National Tsing Hua University}{Hsinchu, Taiwan}
      
    \resumeSubheading
      {FPGA-Based Tetris with Basys 3 Artix-7}{Jun. 2023}  
      {National Tsing Hua University}{Hsinchu, Taiwan}

    \resumeSubheading
      {High-Speed 128x16-bit ROM Macro with Sub-5ns Access Time}{Jan. 2023}  
      {National Tsing Hua University}{Hsinchu, Taiwan}

      
  \resumeSubHeadingListEnd

\section{Skills}
    \textbf{Programming Languages:} Verilog, Python, C/C++, Linux, Git
        
    \textbf{Design Tools:} VCS, Verdi, SpyGlass, DC, PrimeTime, Hspice, Laker, Innovus, Calibre, Virtuoso, Caliber


      
\end{document}