%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Hao-Chun Liang}
\end{center}

 \begin{center}
    \vspace{-3mm}
\small
\href{mailto:science103555@gmail.com}{\underline{Email}} $|$
\href{https://www.linkedin.com/in/hao-chun-noah-liang-131348207/}{\underline{Linkedin}} $|$ 0982-955885
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Yang Ming Chiao Tung University}{Sep. 2025 -- Jun. 2027 (Exp.)}
      {M.Eng. in Institute of Pioneer Semiconductor Innovation (ICS \& EDA Group)}{Hsinchu, Taiwan}


    \resumeSubheading
      {National Tsing Hua University}{Sep. 2021 -- Jun. 2024}
      {B.S. in Electrical Engineering $\vert$ GPA: 4.1/4.3 $\vert$ Distinction Graduation}{Hsinchu, Taiwan}

    \resumeSubheading
      {National Tsing Hua University}{Sep. 2020 -- Jun. 2021}
      {B.S. in Physics $\vert$ Transferred to EE (Top 1 of 65; Elite Student Award)}{Hsinchu, Taiwan}


  \resumeSubHeadingListEnd


%-----------Work Experience-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Digital IC Design Intern}{Nov. 2024 -- Aug. 2025}
      {Andes Technology Corporation $\vert$ Acceleration R\&D Division}{Hsinchu, Taiwan}

    \resumeSubheading
      {Affiliate Trainee (Remote)}{Jun. 2024 -- Present}
      {A3D3 Institute $\vert$ University of Washington}{Washington, U.S.}

    \resumeSubheading
      {Graduate Research Assistant}{Sep. 2025 -- Jun. 2027 (Exp.)}
      {National Yang Ming Chiao Tung University $\vert$ Parallel Computing System Laboratory}{Hsinchu, Taiwan}

  \resumeSubHeadingListEnd


%-----------Awards-----------
\section{Awards \& Certificates}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Excellent Poster Award}{Aug. 2025}
      {Taiwan and Japan Conference on Circuits and Systems (TJCAS)}{Osaka, Japan}

    \resumeSubheading
      {Cell-Based Digital Chip Design and Implementation (ADFP - TSMC 16nm)}{Sep. 2024}
      {Taiwan Semiconductor Research Institute (TSRI)}{Hsinchu, Taiwan}

    \resumeSubheading
      {Distinction Graduation (Top 5\% of 116 in Professional Elective GPA)}{Jun. 2024}
      {National Tsing Hua University $\vert$ Electrical Engineering}{Hsinchu, Taiwan}

    \resumeSubheading
      {College of Science Elite Student Award (Top 1 of 65)}{Apr. 2021}
      {National Tsing Hua University $\vert$ College of Science}{Hsinchu, Taiwan}

  \resumeSubHeadingListEnd


\section{Publications}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Real-Time GPU Kalman-Filter Tracking via Kernel Refactoring and INT8 Surrogates}{}
      {Fast Machine Learning for Science Conference 2025, CERN $\vert$ \textbf{First Author}}{}

    \resumeSubheading
      {An Integrated FPGA Implementation of Complete GNN-Based Trajectory Reconstruction}{}
      {Taiwan and Japan Conference on Circuits and Systems (TJCAS) 2025 $\vert$ Second Author}{}

    \resumeSubheading
      {A High-Performance Implementation of GNN-Based Trajectory Reconstruction on FPGA}{}
      {VLSI Design/CAD Symposium 2025 $\vert$ Second Author}{}

    \resumeSubheading
      {Fine-Grained Image Recognition from Scratch with Teacher-Guided Data Augmentation}{}
      {arXiv $\vert$ Fifth Author}{}

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Regfile Automatic Code Generation}{Nov. 2024 -- Present}
      {Andes Technology Corporation}{Hsinchu, Taiwan}

    \resumeSubheading
      {CUDA Pipeline Optimization for Particle Tracking at HL-LHC}{Jun. 2024 -- Present}
      {A3D3 Institute $\vert$ University of Washington}{Washington, U.S.}

    \resumeSubheading
      {UltraLightweight HDC-CNN for NeurIPS 2025 Weak Lensing Challenge}{2025}
      {NeurIPS FAIR Universe Challenge}{Top-20 Ranking}


  \resumeSubHeadingListEnd

\section{Skills}
    \textbf{Programming Languages:} Python, C/C++, Verilog/SystemVerilog, HLS, CUDA, Perl, Shell

    \textbf{Profiling Tools:} NVIDIA NSYS, NCU

    \textbf{Domains:} Efficient Machine Learning, Computer Architecture, Digital IC Design, RTL/C++ Codegen



\end{document}
